```{r load-packages, message = FALSE}
library(tidyverse)
knitr::opts_chunk$set(error = TRUE)
```

## Words

We'll use the dataset `words`, which is loaded automatically when you load the `stringr` package.  It contains `r length(words)` common English words.


```{r}
word_df = tibble(word = words)
```

1.  How many words contain an "x" anywhere in them? List them.

```{r}
filter(word_df, str_detect(word, PATTERN))
```


2.  How many words end in "x"?  List them.  Use `$` to match the end of the string.

3.  Do any words start with "x"?  Use `^` to match the start of the string.

4.  Using wildcards `.` and quantifiers `+` (rather than the results of the previous exercises), find all the words that contain "x" in the interior (but not at the start or end).  Check that the number of results from 1-4 are coherent.

```{r}
filter(word_df, str_detect(word, '.+x.+'))
```


5.  On average, how many vowels are there per word?  (Hint: use `str_count` and `[]` to define a character class).  What is the average vowel-per-letter (# of vowels normalized per length)

6.  List all the words with three or more vowels in a row.  Use `{min_matches,max_matches}` as a quantifier.

## Sentences

Now, consider the `r nrow(sentences)` in the `sentences` data set:

```{r}
sentence_df = tibble(sentence  = sentences)
```

7.  Extract the first word from each sentence.  Hint: negate the space character class "[ ]" to match everything except a space.

8.  Return all the sentences that contain the colors "red", "blue" or "green".  Use the `|` disjunction.

9.  Extract the first word ending in "s".  Use a capture group `()`, `str_match()` and the everything-but-space `[^ ]` character class.

```{r}
sentence_df = sentence_df %>% mutate(second = str_match(sentence, "([^ ]*s)\\b")[,2])
```


10.  (Stretch goal) Notice that two questions ago, we also matched the sentence

> The colt reared and threw the tall rider.

because "reared" contains "red". Fix the regular expression so it only matches the complete words, not just a fragment using the "\<" word start marker.  Hint:  use <code>r"(...)"</code> to construct a "raw" string -- this protects the backslash from being used as an escape character.
